Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{ Funded by DARPA Cyber Assured Systems Engineering (CASE) contract HR00111890001. }

### 2021-05-06 paper/example.tex
Update with transform patterns

\newsavebox{\flt}
\begin{lrbox}{\flt}
\begin{lstlisting}[style=agree]
eq policy : bool = WELL_FORMED_AUTOMATION_RESPONSE(Input);
property Policy_Output = 
      if event(Input) and policy then 
        event(Output) and Output = Input
      else not event(Output);
guarantee "Filter output is well-formed" :
    Policy_Output;
\end{lstlisting}
\end{lrbox}

\newsavebox{\mntr}
\begin{lrbox}{\mntr}
\begin{lstlisting}[style=agree]
const is_latched : bool = 
  Get_Property(this, CASE_Properties::Monitor_Latched);
eq rsp : bool = event(Response);
eq req : bool = event(Request);
eq nothing : bool = (not req) -> (not pre (req)) and (not req);
eq today : bool = req and rsp;    
eq yesterday : bool = false -> pre (req and not rsp);
eq policy: bool = nothing
                or (today and not yesterday)
                or (not today and rsp and yesterday);
eq alert : bool = (not policy) 
                -> ((is_latched and pre(alert)) or not policy);
property Policy_Output = 
  if event(Alert) then (not event(Output)) else
  if event(Response) then (event(Output) and (Output = Response))
  else (not event(Output));
property Policy_Alert =  event(Alert) = alert;

guarantee "Alert port tracks alert variable" :
    Policy_Alert;
guarantee "Output if not alerted" :
    Policy_Output;
\end{lstlisting}
\end{lrbox}

@@

The system implementation is cyber-hardened by using the CASE tools to insert high-assurance components in the form of a filter and a monitor as shown in \figref{fig:hardened}(a). A filter enforces an invariant over each datum in the data stream by not forwarding input to its output if that input is violating. Its stylized form as generated by the tool is shown in \figref{fig:assurance}(a). The user must declare the meaning of the \texttt{policy} value as part of the transform on the model. In this example, \texttt{policy} is the assumption made by the waypoint manager about the automation response being well-formed. The output policies and guarantees are automatically generated by the tool.

A monitor captures a relation over time on input data and is able to reason about temporal properties of that input. By definition, it raises an alert output when the relation is violated. The generated monitor contract is shown in \figref{fig:assurance}(b). The \texttt{is\_latched} value makes the alert persistent meaning that once raised always raised. The definition for \texttt{policy} is taken from the contract in \figref{fig:sw} since this high-assurance component is the monitor that needs to alert violations of the bounded response policy. As before the policies for the outputs and the guarantees are autogenerated by the tool.

>>>>

\newsavebox{\flt}
\begin{lrbox}{\flt}
\begin{lstlisting}[style=agree]
eq policy : bool = 
  WELL_FORMED_AUTOMATION_RESPONSE(Input);       
guarantee Filter_Output "Filter output is well-formed" :
  if event(Input) and policy then 
    event(Output) and Output = Input
  else not event(Output);
\end{lstlisting}
\end{lrbox}

\newsavebox{\mntr}
\begin{lrbox}{\mntr}
\begin{lstlisting}[style=agree]
const is_latched : bool = 
Get_Property(this, CASE_Properties::Monitor_Latched);
eq rsp : bool = event(Response);
eq req : bool = event(Request);
eq nothing : bool = (not req) -> (not pre (req)) and (not req);
eq today : bool = req and rsp;    
eq yesterday : bool = false -> pre (req and not rsp);
eq policy: bool = nothing
               or (today and not yesterday)
               or (not today and rsp and yesterday);
eq alert : bool = (not policy) 
               -> ((is_latched and pre(alert)) or not policy);
guarantee Monitor_Alert 
  "Alert port tracks alert variable" :
  event(Alert) = alert;
guarantee Monitor_Output
  "Output if not alerted" :
  if event(Alert) then (not event(Output)) else
  if event(Response) then (event(Output) and (Output = Response))
  else (not event(Output));
\end{lstlisting}
\end{lrbox}

@@

The system implementation is cyber-hardened by using the CASE tools to insert high-assurance components in the form of a filter and a monitor as shown in \figref{fig:hardened}(a). A filter enforces an invariant over each datum in the data stream by not forwarding input to its output if that input is violating. Its stylized form as generated by the tool is shown in \figref{fig:assurance}(a). The user must declare the meaning of the \texttt{policy} value as part of the transform on the model. In this example, \texttt{policy} is the assumption made by the waypoint manager about the automation response being well-formed. The output guarantees are automatically generated by the tool.

A monitor captures a relation over time on input data and is able to reason about temporal properties of that input. By definition, it raises an alert output when the relation is violated. The generated monitor contract is shown in \figref{fig:assurance}(b). The \texttt{is\_latched} value makes the alert persistent meaning that once raised always raised. The definition for \texttt{policy} is taken from the contract in \figref{fig:sw} since this high-assurance component is the monitor that needs to alert violations of the bounded response policy. As before the guarantees for the outputs are autogenerated by the tool.

### 2021-05-06 paper/system.tex
Update with transform patterns

\begin{figure}
  \[
    \begin{array}{rcl}
      \mathit{c}    & = & \konst{input}\ [(f : \tau)\ldots] \\
                    &   & \konst{output}\ [(f : \tau)\ldots] \\
                    &   & \konst{eq}\; f : \tau := \mathit{exp} \\
                    &   & \konst{policies}\ [\mathit{bexp}\ldots]\\

@@

The specification language for high-assurance components is in (see \figref{fig:syntax}). It is stylized contracts that defines the inputs, outputs, local values, and policies for each output. Each output policy must be invariant over the input stream and completely define the meaning of its corresponding output. A type $\tau$ is a contiguity type which is a self-describing dependent type specification (add citation). An $\lval$ is a reference to an \emph{L-value} from compiler concepts and is an expression that can appear on the left hand side of an assignment. Alpha renaming is assumed so that every $\lval$ is unique.

@@

The initial environment stream only contains mappings for the inputs along the entire stream. Stepping the component updates the current environment and checks the policies. In other words, at the $i^\mathrm{th}$ step, $\theta^i$ is updated with the result of the sequential evaluation of the \konst{eq}-statements in the specification, which are assumed to be in dependency order, and then the policies are checked for invariance.

>>>>

\begin{figure}
  \[
    \begin{array}{rcl}
      \mathit{c}    & = & \konst{input}\ [(f : \tau)\ldots] \\
                    &   & \konst{output}\ [(f : \tau)\ldots] \\
                    &   & \konst{eq}\; f : \tau := \mathit{exp} \\
                    &   & \konst{guarantees}\ [\mathit{bexp}\ldots]\\

@@

The specification language for high-assurance components is in (see \figref{fig:syntax}). It is stylized contracts that defines the inputs, outputs, local values, and guarantees for each output. Each guarantee must be invariant over the input stream and define the meaning of its corresponding output under all conditions. A type $\tau$ is a contiguity type which is a self-describing dependent type specification (add citation). An $\lval$ is a reference to an \emph{L-value} from compiler concepts and is an expression that can appear on the left hand side of an assignment. Alpha renaming is assumed so that every $\lval$ is unique.

@@

The initial environment stream only contains mappings for the inputs along the entire stream. Stepping the component updates the current environment and checks the policies. In other words, at the $i^\mathrm{th}$ step, $\theta^i$ is updated with the result of the sequential evaluation of the \konst{eq}-statements in the specification, which are assumed to be in dependency order, and then the guarantees are checked for invariance.

The meaning of the specification is a set of finite environment streams where the guarantees hold at each step of the streams and the updated mappings or the \konst{eq}-statements are consistent with the statements.
